---
title: "GEfileformats_annotations"
author: "Ruben Alvarez"
date: "17 July 2017"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document establishes the *file formats* (IncellWestern and Incucyte) that are accepted by the webapp. Both are *tab-delimited* and *.txt* files.  

### IncellWestern file format  
This file must contain a line called "Total Channel 700", with the data from the 96-well plate below, and a line called "Total Channel 800" also with the correspondent 96-well data, as in the example below and file *IncellWestern_fileformat.txt*. Any other lines in the file are ignored.  


```{r kable, echo = F}

df <- as.data.frame(matrix(nrow = 18,
              ncol = 12,
              data = c(
                'Total Channel 700', rep('', 11),
                as.character(round(1200*runif(96), 2)),
                'Total Channel 800', rep('', 11),
                as.character(round(1000*runif(96),2))
                ),
              byrow = TRUE))
                
library(knitr)
kable(df, col.names = rep('',12))

```

### Incucyte file format  
This file must contain a line that starts with "Date Time" (this column contains the time stamp), followed by the time elapsed (this column contains the elapsed hours), and followed by the well locations (these columns contain the %confluence), as in the example below and file *IncuCyte_fileformat.txt*. Any other lines in the file are ignored.  

```{r kable2, echo = F, warnings=TRUE}

df2 <- data.frame(
  'Date Time' = c('13/01/2017 11:00:00', '13/01/2017 14:00:00', '...', '17/01/2017 08:00:00'),
  'Elapsed' = c('0', '3','...', '93'),
  'A1' = c('22.30', '22.44', '...', '85.97'),
  'B2' = c('21.67','23.47', '...', '93.87'),
  'C2' = c('24.37','25.60', '...', '95.45'),
  '...' = c(rep('...', 4)),
  'H12' = c('19.79','20.32', '...', '89.19')
)

library(knitr)
kable(df2)

```

